Main Analyses

### 2016-02-21 Rmd/main-analysis.Rmd
Analyses done through objective weights figure, which uses nearest neighbors and Jaccard Index to assess spatial differences between conversion maps.

```{r, warning=FALSE, message=FALSE}
library(agroEcoTradeoff)
library(readxl)
library(gdalUtils)
library(gisutils)

setwd("~/Dropbox/publications/zambiaToff/private/zambiaToff/")
p_root <- getwd()
p_demand <- fp(p_root, "external/input_devel/demand/")
p_mod <- fp(p_root, "agroEcoTradeoff")
p_moddat <- fp(p_mod, "external/data/ZA")
p_figures <- full_path(p_root, "paper/figures/")
p_roads <- fp(p_root, "external/input_devel/roads")
p_roads2 <- paste0("/Users/lestes/Dropbox/data/zari/infrastructure/zambia/", 
                   "rda_dump/Final Shape files RDA/")
p_out <- fp(p_mod, "external/output")
```

@@

@@

@@

basedt <- soyto$inputs$mask
```

@@

# plot(ybdc$maize$heat)
# par(mfrow = c(1, 2))
# plot(ycost$maize$heat)
# plot(ycost$soy$heat)
# plot(ycost$both$heat)
# plot(bdc$both$heat)
# save(ybdc, cbdc, ycost, bdc, file = fp(p_out, "mainresults1502.rda"))
save(ybdc, ycost, bdc, file = fp(p_out, "mainresults1702.rda"))
# load(fp(p_out, "mainresults1402.rda"))
```

@@

### Figure 1
```{r, eval = FALSE}
# select out results for "pure" cases (weight = 1)
pure <- sapply(cnames, function(x) which(round(ybdc$both$params[, x], 4) == 1))

@@

# For Panel B - impact statistics 
bpath <- fp(p_out, ybdc$both$bcode)
load(fp(bpath, "impacts_tab.rda"))  # get impacts table

# select out corresponding impact statistics, summarize
pure2 <- unlist(lapply(pure, function(x) c(x, x+1)))
vars <- c("iter", "conv_area", "tot_C", "fpa_conv", "mu_cost", "rarity",
          "priority",  "int_prior", "int_mean")
conv_stats <- selected_impacts(pure, fp(p_out, ybdc$both$bcode))
# conv_stats <- outtab[outtab$iter %in% pure, vars]
# conv_stats <- data.frame(t(sapply(pure, function(x) {  # x <- pure[1]
#   DF <- conv_stats[conv_stats$iter == x, ]
#   c(colSums(DF[, 2:4]), 
#     sapply(5:ncol(DF), function(y) weighted.mean(DF[, y], DF$conv_area)))
# }))) 
# colnames(conv_stats) <- vars[-1]

@@

# Plots
# Panel A
# cols <- RColorBrewer::brewer.pal(11, "RdYlBu")
# cols <- colorspace::diverge_hsv(n = 11)
# colsi <- sapply(c(0.5, 0.75, 1), function(x) rgb(1, 1, 0.9, alpha = x))
cols <- c("dodgerblue3", "deepskyblue1", "goldenrod2", "yellow", "tomato1",
          "red3")
plot(1:6, pch = 20, cex = 3, col = cols)

tiff(fp(p_figures, "single_priorities.tif"), height = 3, width = 8, 
     units = "in", res = 300)
par(mfrow = c(1, 3))
imp_plot2(dtr = rs_over_rc2, impacts = i1, fpath = p_figures, 
          fnm = "pure_overlap", cexscale = 0.6, ftitle = "", crops = leg2, 
          stats = FALSE, cols = cols, hold = TRUE, marg = c(0, 0, 0, 0))

@@

#### Need to redo pareto to pass in weighted mean function for all average 
#### costs (DONE)

@@

## Figure 2 & 3 (probably supplemental)
```{r, eval = FALSE}
# yc_bdc_st <- as.matrix(stack(ycost$both$heat, bdc$both$heat) / 100)
# yc_bdc_st <- stack(ycost$both$heat, ycost$both$heat * 0, bdc$both$heat) / 100
# plot(ycost$both$heat > 1)
# plotRGB(yc_bdc_st, r = 1, g = 2, b = 3, colNA = "transparent", scale = 1)
# rgb(red = yc_bdc_st[, 1], rep(0, nrow(yc_bdc_st)), yc_bdc_st[, 2])
# plot(ycost$both$heat)

@@

## Figure 4

Value of just a bit of compromise

```{r, eval = FALSE}
p <- data.frame(ybdc$both$params)
outtab[1, ]
p[, c("Y", "C", "BD" ,"COST")] <- round(p[, c("Y", "C", "BD" ,"COST")], 2)
# scens <- list(c(0.9, 0.05, 0.05, 0), 
#               c(0.85, 0.05, 0.05, 0.05), 
#               c(0.1, 0.45, 0.45, 0.0), 
#               c(0.05, 0.45, 0.45, 0.05))
scens <- lapply(c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9), function(x) {
  c(1 - x, rep(x / 2, 2), 0)
})
# scens <- lapply(c(0, 0.15, 0.3, 0.45, 0.6, 0.75), function(x) {
#   c(1 - x, rep(x / 3, 3))
# })
pind <- sapply(scens, function(x) {
  x <- round(x, 2)
  which(p$Y == x[1] & p$C == x[2] & p$BD == x[3] & p$COST == x[4])
})

# select out impacts corresponding to those runs
cstats <- selected_impacts(pind, p_out, ybdc$both$bcode)

# check on selection
# il <- input_handler(p_moddat, crops[[1]])
# chk <- tradeoff_mod(targ, ybdc$both$params[pind[5], 7:10], 
#                     currprodmod = g, exist_list = il)
# DF <- data.frame(chk$impacts)
# outtab[outtab$iter == pind[5], -2]
# round(c(colSums(DF[, 2:4]),
#         sapply(5:ncol(DF), function(z) weighted.mean(DF[, z], DF$conv_area))), 
#       2)
# cstats[5, ]
outtab[outtab$iter == pind[5], ]
outtab[, 1:4][1:100,]

fnames <- dir(bpath, pattern = "csv")
fnames[pind[5]]

# calculate max impacts across both crops, and figure out the impact range, 
# and what percent that is relative to the worst case
allstats <- selected_impacts(1:nrow(p), p_out, ybdc$both$bcode)
minmaxstats <- allstats[, lapply(.SD, range)]
imp_range <- minmaxstats[, lapply(.SD, diff)]  # difference between best/worst
pct_of_tot <- minmaxstats[, lapply(.SD, function(x) diff(x) / max(x))]

@@

plot(imp_pct$tot_C, imp_pct$conv_area, type = "l", xlab = "", ylab = "", 
     axes = FALSE)        # xaxs = "r", yaxs = "r")

@@

scens_r <- lapply(pind, function(x) {  # x <- pind[[1]]
  print(x)
  inm <- paste0(outtab[outtab$iter == x, "rc"][1], ".csv")
  fpath <- fp(fp(p_out, ybdc$both$bcode), inm)
  # fname <- dir(bpath, pattern = "csv", full.names = TRUE)[x]
  DT <- cbind(fread(fpath), basedt[, .(x, y, convertible)])
  DTr <- dt_to_raster(DT, CRSobj)
})

scens_rs2 <- lapply(scens_r, function(x) calc(stack(x[[1:2]]), sum))
# freq((rs2$Y + scens_rs2[[1]]) * scens_r[[1]]$convertible
# plot(scens_rs2[[1]] + scens_rs2[[2]])

# round(sapply(scens_rs2, function(x) {
#   cellStats(x * scens_r[[1]]$convertible * 100, sum)
# }))
# cstats$conv_area

@@

# overlap areas
scens_over_a <- sapply(1:length(scens_over), function(x) { # x <- 4
  sapply(1:3, function(y) {  # y <- 3
    r <- scens_over[[x]] == y
    # plot(r)
    round(cellStats(r * scens_r[[1]]$convertible, sum), 1)
  })
})
sum(scens_over_a[c(2, 3), 4])
# over_cols <- sapply(seq(0, 0.4, 0.1), function(x) rgb(1 - x, 0, x))
# par(mar = c(0, 0, 0, 0))
# plot(1:3, pch = 20, col = rgb(1, 0, 1))
# plot(zambia)

cols <- c("grey", c(rgb(0, 1, 0), rgb(0, 0, 1), rgb(1, 0, 1)))
ftits <- c("Y=0.9")
par(mfrow = c(1, 4))
for(i in 1:4) {
  plot(zambia)
  imp_plot2(scens_over[[i]], impacts = i1, fpath = p_figures, fnm = "bob", 
            col = cols, add = TRUE, 
            legend = FALSE)
}
plot(scens_over[[1]], col = c("transparent", over_cols[[5]]))
plot(scens_rs2[[1]])
plot(scens_over[[4]])
plot(calc(stack(scens_over), sum))

plot(calc(stack(scens_rs2[2:4]), sum))

ybdc$both$optimal[, {
  par(mfrow = c(2, 2), mar = rep(3, 4))
  hist(.SD, axes = FALSE, labels = FALSE)
}, .SDcol = 1:4]

frange <- function(x) diff(range(x)) / max(x)
fqtile <- function(x) diff(quantile(x, probs = c(0.025, 0.975))) / max(x) 
ybdc$both$optimal[, lapply(.SD, frange), .SDcol = 1:4]
ybdc$both$optimal[, lapply(.SD, fqtile), .SDcol = 1:4]

hist(ybdc$both$optimal$Y)

>>>>

```{r, warning=FALSE, message=FALSE}
library(agroEcoTradeoff)
library(readxl)
library(gdalUtils)
library(gisutils)
# URL <- paste0("https://cran.r-project.org/src/contrib/Archive/spatstat/",
#               "spatstat_1.42-2.tar.gz")
# install.packages(URL, repos = NULL, type="source", dependencies = TRUE)
library(spatstat)

setwd("~/Dropbox/publications/zambiaToff/private/zambiaToff/")
p_root <- getwd()
p_demand <- fp(p_root, "external/input_devel/demand/")
p_mod <- fp(p_root, "agroEcoTradeoff")
p_moddat <- fp(p_mod, "external/data/ZA")
p_figures <- full_path(p_root, "paper/figures/")
p_other <- fp(p_root, "external/input_devel/other/")
p_roads <- fp(p_root, "external/input_devel/roads")
p_roads2 <- paste0("/Users/lestes/Dropbox/data/zari/infrastructure/zambia/", 
                   "rda_dump/Final Shape files RDA/")
p_out <- fp(p_mod, "external/output")
```

@@

# farmblocks
fbp <- "/Users/lestes/Dropbox/data/zari/misc/NEW4GEO/Fblocks.sqlite"
# fb <- readOGR(fbp, layer = "fblocks")
# fbalb <- spTransform(fb, mgrid@crs)
# fbalb$ID <- 1:nrow(fbalb)
# fbalb@data <- fbalb@data[, "ID", drop = FALSE]
fnm <- fp(p_other, "fblocks_alb.sqlite")
# writeOGR(fbalb, dsn = fnm, layer = "fblocks_alb", driver = "SQLite")

# read in farmblocks
fbalb <- readOGR(fnm, layer = "fblocks_alb")
fbr <- rasterize(fbalb, mgrid)
fbr[is.na(fbr)] <- 0
fbr[fbr > 0] <- 1
fbr <- raster::mask(fbr, mgrid)
# plot(fbr)

@@

<a href="#top">Back to top</a>

@@

basedt <- soyto$inputs$mask
```
<a href="#top">Back to top</a>

@@

# plot(ybdc$maize$heat)
# par(mfrow = c(1, 2))
# plot(ycost$maize$heat)
# plot(ycost$soy$heat)
# plot(ycost$both$heat)
# plot(bdc$both$heat)
# save(ybdc, cbdc, ycost, bdc, file = fp(p_out, "mainresults1502.rda"))
save(ybdc, ycost, bdc, file = fp(p_out, "mainresults1702.rda"))
# load(fp(p_out, "mainresults1702.rda"))
```

<a href="#top">Back to top</a>

@@

### Figure 1
```{r, eval = FALSE}
# select out results for "pure" cases (weight = 1)
cnames <- c("Y", "C", "BD", "COST")
pure <- sapply(cnames, function(x) which(round(ybdc$both$params[, x], 4) == 1))

@@

# For Panel B - impact statistics 
# bpath <- fp(p_out, ybdc$both$bcode)
# load(fp(bpath, "impacts_tab.rda"))  # get impacts table

# select out corresponding impact statistics, summarize
pure2 <- unlist(lapply(pure, function(x) c(x, x + 1)))
vars <- c("iter", "conv_area", "tot_C", "fpa_conv", "mu_cost", "rarity",
          "priority",  "int_prior", "int_mean")
conv_stats <- selected_impacts(pure, fp(p_out, ybdc$both$bcode))

@@

# Plots
# Panel A
# cols <- RColorBrewer::brewer.pal(11, "RdYlBu")
# cols <- colorspace::diverge_hsv(n = 11)
# colsi <- sapply(c(0.5, 0.75, 1), function(x) rgb(1, 1, 0.9, alpha = x))
cols <- c("dodgerblue3", "deepskyblue1", "goldenrod2", "yellow", "tomato1",
          "red3")
# plot(1:6, pch = 20, cex = 3, col = cols)

tiff(fp(p_figures, "single_priorities.tif"), height = 3, width = 8, 
     units = "in", res = 300)
par(mfrow = c(1, 3))
imp_plot2(dtr = rs_over_rc2, impacts = i1, fpath = p_figures, 
          fnm = "pure_overlap", cexscale = 0.5, ftitle = "", crops = leg2, 
          stats = FALSE, cols = cols, hold = TRUE, marg = c(0, 0, 0, 0))

@@

@@

<a href="#top">Back to top</a>

### Figures 2 & 3 (probably supplemental)
```{r, eval = FALSE}
# yc_bdc_st <- as.matrix(stack(ycost$both$heat, bdc$both$heat) / 100)
# yc_bdc_st <- stack(ycost$both$heat, ycost$both$heat * 0, bdc$both$heat) / 100
# plot(ycost$both$heat > 1)
# plotRGB(yc_bdc_st, r = 1, g = 2, b = 3, colNA = "transparent", scale = 1)
# rgb(red = yc_bdc_st[, 1], rep(0, nrow(yc_bdc_st)), yc_bdc_st[, 2])
# plot(ycost$both$heat)

@@

<a href="#top">Back to top</a>

### Figures 4 (main) and 5 (probably supplemental)

What happens when weight is progressively added

```{r, eval = FALSE}
p <- data.frame(ybdc$both$params)
p[, c("Y", "C", "BD" ,"COST")] <- round(p[, c("Y", "C", "BD" ,"COST")], 2)
# scens <- list(c(0.9, 0.05, 0.05, 0), 
#               c(0.85, 0.05, 0.05, 0.05), 
#               c(0.1, 0.45, 0.45, 0.0), 
#               c(0.05, 0.45, 0.45, 0.05))
scens <- lapply(c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9), function(x) {
  c(1 - x, rep(x / 2, 2), 0)
})
# scens <- lapply(c(0, 0.15, 0.3, 0.45, 0.6, 0.75), function(x) {
#   c(1 - x, rep(x / 3, 3))
# })
pind <- sapply(scens, function(x) {
  x <- round(x, 2)
  which(p$Y == x[1] & p$C == x[2] & p$BD == x[3] & p$COST == x[4])
})

# select out impacts corresponding to those runs
cstats <- selected_impacts(pind, fp(p_out, ybdc$both$bcode))

# check on selection
# il <- input_handler(p_moddat, crops[[1]])
# chk <- tradeoff_mod(prod_targ = targ, cbetas = ybdc$both$params[pind[5], 7:10], 
#                     currprodmod = g, exist_list = il)
# DF <- data.frame(chk$impacts)
# outtab[outtab$iter == pind[5], -2]
# round(c(colSums(DF[, 1:2]),
#         sapply(4:ncol(DF), function(z) weighted.mean(DF[, z], DF$conv_area))),2)
# cstats[5, ]
# outtab[outtab$iter == pind[5], ]
# fnames <- dir(bpath, pattern = "csv")
# fnames[pind[5]]

# calculate max impacts across both crops, and figure out the impact range, 
# and what percent that is relative to the worst case
allstats <- selected_impacts(1:nrow(p), fp(p_out, ybdc$both$bcode))
minmaxstats <- allstats[, lapply(.SD, range)]
imp_range <- minmaxstats[, lapply(.SD, diff)]  # difference between best/worst
pct_of_tot <- minmaxstats[, lapply(.SD, function(x) diff(x) / max(x))]

@@

# plot(imp_pct$tot_C, imp_pct$conv_area, type = "l", xlab = "", ylab = "", 
#      axes = FALSE)        # xaxs = "r", yaxs = "r")

@@

fnames <- fp(fp(p_out, ybdc$both$bcode), 
             imp_sorter(fp(p_out, ybdc$both$bcode), inds = pind))
scens_r <- lapply(fnames, function(x) {  # x <- pind[[1]]
  print(x)
  DT <- cbind(fread(x), basedt[, .(x, y, convertible)])
  DTr <- dt_to_raster(DT, CRSobj)
})

scens_rs2 <- lapply(scens_r, function(x) calc(stack(x[[1:2]]), sum))
# plot(scens_rs2[[1]] + scens_rs2[[2]])
# check
# round(sapply(scens_rs2, function(x) {
#   cellStats(x * scens_r[[1]]$convertible * 100, sum)
# }))
# cstats$conv_area

@@

# overlap areas
scens_over_a <- sapply(1:length(scens_over), function(x) { # x <- 4
  sapply(1:3, function(y) {  # y <- 3
    r <- scens_over[[x]] == y
    # plot(r)
    round(cellStats(r * scens_r[[1]]$convertible, sum), 1)
  })
})
# colSums(scens_over_a[c(2, 3), ])
# over_cols <- sapply(seq(0, 0.4, 0.1), function(x) rgb(1 - x, 0, x))
# par(mar = c(0, 0, 0, 0))
# plot(1:3, pch = 20, col = rgb(1, 0, 1))
# plot(zambia)

# cols <- c(rgb(1, 0, 0), rgb(0, 0, 1), rgb(0.75, 0, 0.75))
cols <- c("red", "blue", "gold")
plot(1:3, pch = 20, col = cols, cex = 20)
ftits <- list("Y 90% C 5% Biod 5% Cost 0%",
              "Y 80% C 10% Biod 10% Cost 0%",
              "Y 70% C 15% Biod 15% Cost 0%",
              "Y 60% C 20% Biod 20% Cost 0%")
leg <- c("Y", "YCBd", "Y + YCBd")

tiff(fp(p_figures, "changing_weights.tif"), height = 4, width = 7, 
     units = "in", res = 300)
par(mfrow = c(2, 4), oma = c(0, 0, 1, 0))
for(i in 1:4) { # i <- 1
  # map
  imp_plot2(scens_over[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
            crops = leg[c(1, 3, 2)], ftitle = ftits[[i]], col = cols, 
            legend = TRUE, hold = TRUE, stats = FALSE, cexscale = 0.4, 
            marg = rep(0, 4))
  # barplot
  par(mar = c(5, 4, 3, 3))
  overl <- scens_over_a[1:3, i][c(1, 3, 2)]
  bp <- barplot(overl, las = 2, ylim = c(0, 12000),  
                col = cols[c(1, 3, 2)], mgp = c(1.5, 0.25, 0), tcl = -0.2, 
                ylab = expression(km^2), cex.axis = 0.6, cex.lab = 0.7)
  axis(side = 1, at = bp, labels = leg, las = 2, 
       mgp = c(1, 0.25, 0), tcl = -0.2, cex.axis = 0.6)
}
dev.off()

```
<a href="#top">Back to top</a>

### Figure 6

Objective weighting of outcomes, based on range of potential impacts

```{r, eval = FALSE}
# objective weights
obj_wgts <- round(pct_of_tot[, {
  c(conv_area, tot_C, int_mean, mu_cost) / 
    sum(c(conv_area, tot_C, int_mean, mu_cost))
}], 2)
# round(obj_wgts, 2)
names(obj_wgts) <- cnames

# Objective weights
toobj <- tradeoff_mod(targ, cbetas = obj_wgts, currprodmod = g, it = "OBJ")

# ybdc$both$params[1, ]
# yp <- ybdc$both$params[, 7:10]
# which(round(yp[, 1], 2) == 0.05 & round(yp[, 2], 2) == 0.30 & 
#         round(yp[, 3], 2) == 0.25 & round(yp[, 4], 2) == 0.4)

# objective weights on ag only 
# considering that these might be two sides of the same coin
ag_wgts <- round(obj_wgts[c(1, 4)] / sum(obj_wgts[c(1, 4)]), 2)
ag_wgts <- c(ag_wgts[1], "C" = 0, "BD" = 0, ag_wgts[2])
ag_wgts2 <- ag_wgts[c(4, 2:3, 1)]
names(ag_wgts2) <- names(ag_wgts)

toag <- tradeoff_mod(targ, cbetas = ag_wgts, currprodmod = g, it = "AGOBJ")
toag2 <- tradeoff_mod(targ, cbetas = ag_wgts2, currprodmod = g, it = "AGOBJ2")

# subjective weights, where we want to treat everyone equally
subj_wgts <- rep(0.25, 4)
names(subj_wgts) <- cnames  # rename to make sure model runs properly
tosubj <- tradeoff_mod(targ, cbetas = subj_wgts, currprodmod = g, it = "SUBJ")

# extract impacts of these, and add in BAU case
tores <- lapply(list(toag, toag2, toobj, tosubj), function(x) {  # x <- toobj
  DTsum <- data.table(x$conv[, rowSums(.SD), .SDcols = c(crops[[1]])])
  DTspat <- cbind(basedt[, .(x, y)], DTsum)
  DTr <- dt_to_raster(DTspat, CRSobj)
  DTr <- DTr + (fbr * 2)  # overlap with farmblocks, for output
  list("map" = DTr, "imp" = x$impacts)
})
names(tores) <- c("ag", "ag2", "obj", "subj")

Calculate area of overlaps between farmblocks and 
yfbr <- calc(mzsoytor, sum) + fbr * 2
plot(yfbr)
fb_over_a <- sapply(1:length(tores), function(x) { # x <- 4
  sapply(1:3, function(y) {  # y <- 3
    r <- tores[[x]]$map == y
    round(cellStats(r * scens_r[[1]]$convertible, sum), 1)
  })
})
fb_sim <- fb_over_a[3, ] / colSums(fb_over_a)

# grid for calculating overlaps
pms2a <- expand.grid(rep(list(0:1), 4))[-1, ] 
pms2b <- pms2a[which(rowSums(pms2a) == 2), ]
pms2b$cl <- c("AgAg2", "AgObj", "Ag2Obj", "AgSubj", "Ag2Subj", "ObjSubj")

toresr <- lapply(tores, function(x) {
  r <- x$map
  r[r == 2] <- 0
  r[r == 3] <- 1
  r
})

# tores_over_r <- lapply(1:nrow(pms2b), function(x) {  # apply logic tests
#   (toresr[[1]] == pms2b[x, 1]) & (toresr[[2]] == pms2b[x, 2]) & 
#     (toresr[[3]] == pms2b[x, 3]) & (toresr[[4]] == pms2b[x, 4])
# })
# names(tores_over_r) <- pms2b$cl
# tores_overs <- stack(tores_over)
tores_over_r <- lapply(1:nrow(pms2b), function(x) {  # apply logic tests
  calc(stack(toresr[which(pms2b[x, ] == 1)]), sum)
})
names(tores_over_r) <- pms2b$cl

# jaccard's similarity, per https://gist.github.com/jlehtoma/3369793
tores_over_a <- sapply(1:length(tores_over_r), function(x) { # x <- 4
  sapply(1:2, function(y) {  # y <- 3
    r <- tores_over_r[[x]] == y
    round(cellStats(r * scens_r[[1]]$convertible, sum), 1)
  })
})
pms2b$JS <- round(tores_over_a[2, ] / colSums(tores_over_a), 3)

# calculate nearest neighbor distance between each version, using spatstat 
# nncross
# plot(zam_owin)
zam_owin <- owin(xrange = bbox(zambia)[1, ], yrange = bbox(zambia)[2, ],
                 unitname = "meter")
which1 <- function(x) x == 1  # selector function for r to xy
tores_nn <- lapply(1:nrow(pms2b), function(x) {  # apply logic tests; x = 2
  ind <- which(pms2b[x, 1:4] == 1)
  rl <- toresr[ind]
  rxy <- lapply(rl, function(x) rasterToPoints(x, fun = which1))
  pps <- lapply(rxy, function(x) {
    ppp(x = x[, 1], y = x[, 2], window = zam_owin)
  })
  # reorder to find which has most points, to put that in as X
  reord <- sort(sapply(pps, function(x) x$n), decreasing = TRUE)
  ppnn <- nncross(pps[[names(reord)[1]]], pps[[names(reord)[2]]])
})
pms2b$NND <- round(sapply(tores_nn, function(x) mean(x$dist))) / 1000
# with(pms2b, plot(NND, JS))

# tores_over_a <- lapply(1:nrow(pms2a), function(x) {  # apply logic tests
#   (toresr[[1]] == pms2a[x, 1]) & (toresr[[2]] == pms2a[x, 2]) & 
#     (toresr[[3]] == pms2a[x, 3]) & (toresr[[4]] == pms2a[x, 4])
# })
# names(tores_over_a) <- pms2a$cl

# colst <- c(rgb(1, 0, 0),   # Ag
#            rgb(1, 0.5, 0),  # Ag 2
#            rgb(1, 1, 0),   # Ag1 and 2
#            rgb(0, 0, 1),  # Obj
#            rgb(1, 0, 1),  # Ag1 and Obj
#            rgb(1, 0.5, 1),  #  Ag2 and Obj
#            rgb(1, 1, 0.5),  #  Ag, Ag2 and Obj
#            rgb(0, 0.5, 1),  # Subj
#            rgb(0, 1, 1),  # Ag and Subj
#            rgb(0, 1, 1),  # Ag2 and Subj
#            rgb(0, 1, 1),  # Ag, Ag2, Subj
#            rgb(0, 1, 1),  # Obj and Subj
#            rgb(0, 1, 1),  # Ag,  Obj and Subj
#            rgb(0, 1, 1),  # Ag2,  Obj and Subj
#            rgb(0, 1, 1))  # All
# plot(1:length(colst), pch = 20, cex = 3, col = colst)

# colst <- c(rgb(0, 1, 1), 
#            rgb(0, 0.5, 1), 
#            rgb(0, 0, 1))
# colst <- c(rgb(1, 1, 0), 
#            rgb(1, 0.5, 0), 
#            rgb(1, 0, 0))

# do sum factoring in overlaps

# sapply(tores_over_r, function(x) {
#   round(cellStats(x * scens_r[[1]]$convertible, sum), 1)
# })

# toressr <- calc(stack(toresr), sum)
# plot(toressr)
# freq(toressr)

# plot(toresr$ag2)
# plot(tores$obj$map - tores$subj$map)

# cols_tr <- c(rgb(1, 0.5, 0, alpha = 0.5), rgb(1, 0, 0, alpha = 0.5), 
#              rgb(0, 0.5, 1, alpha = 0.5), rgb(0, 0, 1, alpha = 0.5))
cols_tr <- c(rgb(1, 0, 0), rgb(1, 0.75, 0), rgb(0, 0, 1), rgb(0, 0.75, 1))
plot(1:4, cex = 3, pch = 20, col = cols_tr)

# par(mfrow = c(2, 2), mar = rep(0, 4))
# # plot(tores$ag$map, col = c("grey", cols_tr[1]), axes = FALSE, legend = FALSE)
# for(i in 1:4) {
#   plot(zambia, col = "grey")
#   plot(toresr[[i]], col = c("transparent", cols_tr[i]), add = TRUE) 
# }
                   # add = TRUE, legend = FALSE)
# plot(toresr[[4]])

# impact table
imp_list <- list(toag$impacts, toag2$impacts, toobj$impacts, tosubj$impacts)
imps <- rbindlist(lapply(imp_list, function(x) selected_impacts2(x)))
impsr <- lapply(c(1, 4, 2, 6:8, 3), function(x) imps[[x]])

# layout matrix
m1 <- do.call(cbind, lapply(1:4, function(x) matrix(rep(x, 35), 5, 7)))
m2 <- matrix(rep(5, 20), 4, 5)
m3 <- do.call(cbind, lapply(6:12, function(x) matrix(rep(x, 12), 4, 3)))
lmat <- rbind(m1, cbind(rep(5, 4), m2, m3, rep(13, 4)))

# plot(1:10, ylab = ylabs[2])
# ylabs <- c("Jaccard Index", 
ylabs <- c(expression(paste("Converted area (", 10^5, " ", km^2, ")")), 
           "Hours", "C loss (Mt)", "Priority", "Intactness/priority",
           "Intactness", expression(paste("FR converted (ha"^2, ")")))
# yscale <- c(1, 10^5, 1, 100000, 1, 1, 1, 1)
yscale <- c(10^5, 1, 100000, 1, 1, 1, 1)
ftits <- list("Y 11% C 0% Biod 0% Cost 89%",
              "Y 89% C 0% Biod 0% Cost 11%",
              "Y 5% C 29% Biod 25% Cost 41%",
              "Y 25% C 25% Biod 25% Cost 25%")
leg <- c("Converted")

# yaxes <- list(seq(0, 0.8, 0.1), seq(0, 14, 2), seq(0, 2.5, 0.5), 
yaxes <- list(seq(0, 14, 2), seq(0, 2.5, 0.5),               
              seq(0, 1000, 200), seq(0, 0.2, 0.05), seq(0, 0.5, 0.1), 
              seq(0, 0.8, 0.2), seq(0, 3500, 500))
# bcols <- c(list(c(cols_tr[1], cols_tr[1], cols_tr[2], cols_tr[1], cols_tr[2],
bcols <- c(list(c(cols_tr[1], cols_tr[2], cols_tr[1], cols_tr[2], 
                cols_tr[3])), lapply(1:7, function(x) rep("black", 4)))
# lcols <- c(list(c(cols_tr[2], cols_tr[3], cols_tr[3], cols_tr[4], cols_tr[4] 
# lcols <- lapply(1:7, function(x) cols_tr)

tiff(fp(p_figures, "objective_weights.tif"), height = 3.5, width = 7, 
     units = "in", res = 300)
l <- layout(mat = lmat)
# layout.show(l)

# map plots
for(i in 1:4) { # i <- 1
  # map
  # plot(zambia)
  imp_plot2(toresr[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
            crops = leg, ftitle = ftits[[i]], col = cols_tr[[i]], 
            legend = TRUE, hold = TRUE, stats = FALSE, cexscale = 0.4, 
            marg = rep(0, 4))
}

# impact plots
mgp <- c(1, 0.25, 0)
par(mar = c(4, 3, 0, 0))
with(pms2b, {
     plot(NND, JS, col = cols_tr[c(2, 3, 3, 4, 4, 4)], pch = 16, cex = 1.5, 
          axes = FALSE, xlab = "", ylab = "", ylim = c(0, 1))
     points(NND, JS, col = cols_tr[c(1, 1, 2, 1, 2, 3)], pch = 20, cex = 1)
     axis(1, at = seq(0, 130, 10), cex.axis = 0.6, las = 2, mgp = mgp, 
          tcl = -0.2)
     axis(2, at = seq(0, 1, 0.1), cex.axis = 0.6, las = 2, mgp = mgp, 
          tcl = -0.2)
     mtext(text = "NN Distance (km)", side = 1, line = 1, cex = 0.45)
     mtext(text = "Jaccard Index", side = 2, line = 1, cex = 0.45)
})
for(i in 1:7) {
  v <- impsr[[i]] / yscale[i]
  b <- barplot(impsr[[i]] / yscale[i], las = 2,  col = cols_tr, 
               mgp = c(1.5, 0.25, 0), tcl = -0.2, yaxt = "n", 
               ylim = range(yaxes[[i]]), ylab = ylabs[i], cex.axis = 0.5,
               cex.lab = 0.7)
  axis(2, at = yaxes[[i]], cex.axis = 0.6, las = 2, mgp = mgp, 
       tcl = -0.2)
}
dev.off()

# ybdc$both$optitab[, {
#   par(mfrow = c(2, 2), mar = rep(3, 4))
#   hist(.SD, axes = FALSE, labels = FALSE)
# }, .SDcol = 1:4]
# 
# frange <- function(x) diff(range(x)) / max(x)
# fqtile <- function(x) diff(quantile(x, probs = c(0.025, 0.975))) / max(x) 
# ybdc$both$optimal[, lapply(.SD, frange), .SDcol = 1:4]
# ybdc$both$optimal[, lapply(.SD, fqtile), .SDcol = 1:4]
# 
# hist(ybdc$both$optimal$Y)
